\documentclass[a4paper,10pt]{article}
\usepackage{cv,booktabs,fontawesome}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% Change color to blue
\def\headcolor{\color[rgb]{0,0,0.5}}

% Space before section headings
\titlespacing{\section}{0pt}{3ex}{1ex}

\name{Samsara Counts}

\info{
% \faicon{map-marker} & Department of Econometrics \& Business
%                                Statistics, Monash University, VIC 3800, Australia.\\
      \faicon{home}       & samsaranc.github.io\\
      \faicon{phone}      & +1 817 994 9732\\
      \faicon{envelope}   & samsaranc@gmail.com\\
      \faicon{twitter}    & @samsaranc\\
      \faicon{github}     & samsaranc}

\bibliography{sncpubs,sncreports}

\DeclareSourcemap{
  \maps[datatype=bibtex, overwrite]{
    \map{
      \step[fieldset=month, null]
    }
  }
}

% Use useprefix because of Ashton de Silva
\ExecuteBibliographyOptions{useprefix=true}

\usepackage[sfdefault,lf,t]{carlito}
\renewcommand{\bibfont}{\normalfont\fontsize{10}{12.4}\sffamily}
\usepackage{inconsolata}

\makebibcategory{reports}{Statistical consulting reports}
\makebibcategory{nonstat}{Poetry}
\makebibcategory{inprogress}{Working papers}


\addtocategory{books}{
  MWH3,
  ITSM91,
  ITSM94,
  expsmooth08,
  fpp,
  unbelievable}

\addtocategory{papers}{
  BHG91,
  BH92,
  YW93,
  Hyndman94,
  HDRF95,
  HDR96,
  HBG96,
  HF96,
  GHH97,
  HW97,
  LFSH97,
  GH98,
  FHV00,
  GHTT00,
  HG00,
  BH01,
  EH01,
  Hyndman01,
  lemmings,
  CHW02,
  HKSG02,
  HY02,
  RH02,
  HH03,
  HB03,
  RLH03,
  HHF04,
  Hyndman04,
  SHW04,
  SKHO04,
  BHK05,
  EH05,
  HKPB05,
  HKOS05,
  SH05,
  ijf25,
  NPS06,
  Hyndman06,
  HK06,
  KH06,
  MH06,
  WSH06,
  ZKH06,
  LCcomparison,
  YH06,
  KSH07,
  EHG07,
  HU07,
  NPS07,
  shortseasonal,
  pollen07,
  Gould08,
  MBH08,
  HAA08,
  austourism,
  HB08,
  HK08,
  hiertourism,
  WSH09,
  AHO09,
  dSHS09,
  OKSH09,
  HS09,
  HS10,
  HF10,
  VHNC10,
  EAGE+10,
  VISTS10,
  YHE10,
  VHZC10,
  KH10,
  SH11,
  Pearce10b,
  longrun,
  FH10b,
  AH11,
  hierarchical,
  AHSW11,
  SBH11,
  Pearce10a,
  DHS11,
  Carta2011,
  HBY13,
  EUHSA12,
  FH11,
  mapcah12,
  gefcom,
  foresight14,
  acfplots14,
  fungal14,
  jaci2015,
  lagphase,
  baggedETS,
  dynamicpareto,
  gefcom2014,
  fasthts,
  smart-meter-quantiles,
  Tham2016,
  m3pca,
  hfts,
  pearce2016exploring,
  handguns,
  fvanaive,
  temporal-hierarchies,
}

\addtocategory{chapters}{
  AGH95,
  ISGMS02a,
  ISGMS02b,
  ISGMS02c,
  HS08,
  IESS10a,
  IESS10b,
  IESS10c,
  BHT14,
  saschapter,
  saschapter2,
  sampling-multiobjective-optimization}

\addtocategory{conferences}{
  NAGS86,
  ESAM99,
  IWSM01,
  ISI05,
  WSH05,
  SH09,
  laura1,
  Han10,
  FH10,
  boostingar,
  epic,
  iwfos14,
  cikm2015,
  probhts,
  }

\addtocategory{inprogress}{
  bivarridges,
  ropes,
  tscv,
  str,
  kdd2015,
  participationrates,
  mint,
  BayesianRankVAR,
  ausmacrodata,
  ausmacrofcast}

\addtocategory{bookreviews}{
  BR96,
  BR98a,
  BR98b,
  BR99a,
  BR99b,
  BR99c,
  BR00,
  EH05a}

\addtocategory{editorials}{
  IJFeditorial05,
  IJFeditorial06,
  IJFeditorial10a,
  IJFeditorial10b,
  tourismeditorial11,
  hyndman2015change,
  usertalk11,
  IJFeditorial13,
  hyndman2015new}

\addtocategory{phd}{phd}

\addtocategory{software}{
  Raddb,
  Ranomalous,
  Rbfast,
  Rdemography,
  Reechidna,
  Remma,
  Rexpsmooth,
  Rfds,
  Rfma,
  Rforecast,
  Rfpp,
  Rftsa,
  Rhdrcde,
  Rhts,
  RMcomp,
  RMEFM,
  Rrainbow,
  RsmoothAPC,
  RstR,
  Rthief,
}

\begin{document}
\maketitle

\section{Education}

~\begin{tabular}{lll}
1988 & B.Sc.(Hons) & University of Melbourne %\\
% 1992 & Ph.D. & University of Melbourne\\
% 2000 & A.Stat. & Statistical Society of Australia.
\end{tabular}


\section{Current positions}

~\begin{tabular}{lP{15cm}}
2003--& \textbf{Professor of Statistics},
        Department of Econometrics \& Business Statistics, Monash University.\\
2005--& \textbf{Director},
        International Institute of Forecasters.\\
2005--& \textbf{Editor-in-Chief},
        \textit{International Journal of Forecasting}.\\
2011--& \textbf{Editor}, \textit{Journal of Statistical Software}.\\
%2001--& \textbf{Director, Business \& Economic Forecasting Unit},
%        Department of Econometrics \& Business Statistics, Monash University.\\
1999--& \textbf{Director of Consulting},
        Department of Econometrics \& Business Statistics, Monash University.
\end{tabular}



\section{Honors and awards}

~\begin{tabular}{ll}
%2017 & Visiting Expert Professor, Chinese Academy of Sciences, Beijing, China.\\
2016 & KNAW Visiting Professor, TU/Eindhoven, Netherlands.\\
2010 & Dean's Award for excellence in innovation and external collaboration, Monash University.\\
2010 & HP Innovation Research Award.\\
1986 & Second Maurice H.\ Belz Prize in Statistics, University of Melbourne
\end{tabular}

\section{Membership of Associations}

~\begin{tabular}{@{~$\bullet$~~}l}
Member, Association for Computing Machinery\\
Member, American Mathematical Society\\
\end{tabular}

\section{Research}

\begin{itemize}\parskip=0cm
% \item Since 1991 I have authored \ref{sumpapers} papers, chapters or books on statistical topics. A list of these appears on pages \pageref{papersstart}--\pageref{papersend}.
\item I have received several awards for my research including the 2007 Moran Medal from the Australian Academy of Science.
\item  My current research projects include forecasting electricity demand, forecasting large collections of time series, and strategies for improving forecasts through bagging and boosting.
\item In 2008 I won the Monash Vice-Chancellor's award for postgraduate supervisor of the year.
% \item I have produced \ref{sumsoftware} R packages as a result of my research. These are listed on page~\pageref{sumsoftware}.
\end{itemize}

\clearpage

\section{Grants}
I have acquired (in most cases jointly) about \$4 million in external research grants since 2000.\vspace*{0.3cm}

{\def\next{\\\\[-0.2cm]}\fontsize{10}{12pt}\selectfont
\begin{tabular}{@{}lP{13.3cm}r@{}}
% \toprule
2009 & Choi, C., R.J. Hyndman, L. Smith and K. Zhao ``An enhanced mortality database for estimating indigenous life expectancy: a feasibility study.'' \emph{Funding from the Australian Institute of Health and Welfare.} &\$10,500
\next
2009--2011 & Erbas, B., Abramson, M., Tang, M., Allen, K., Newbigin, E., Dharmage, S., Hyndman, R.J. ``The impact of outdoor aeroallergen exposure on asthma exacerbations in children and adolescents''. \emph{Funding from the National Health and Medical Research Council.} &\$454,550
% \bottomrule
\end{tabular}}

\clearpage

\section{Major invited talks}

\begin{compactitem}\itemsep=0.1cm
\item Belz lecture, \emph{Forecasting and the importance of being uncertain}, Statistical Society of Australia, Melbourne, October 2006.
\item Knibbs lecture, \emph{Population forecasting and the importance of being uncertain}, Statistical Society of Australia, Melbourne, November 2007.
\item Invited speaker, \emph{Advances in automatic time series forecasting}, Australian Statistics Conference, Adelaide, July 2012.
\end{compactitem}


\section{Teaching}

\begin{compactitem}\itemsep=0.1cm

\item In 1998, I received the award for ``Excellence in teaching'' by the Monash Science Society. This is awarded by the students of the Science faculty.

\end{compactitem}

\section{Advisory boards}

%I am on several scientific advisory boards for external organizations:
\begin{compactitem}
\item Member of the Scaling committee, Victorian Tertiary Admissions Centre. This committee is responsible for producing the ATAR for VCE students.
\item Member of the Methodology Advisory Committee for the Australian Bureau of Statistics.
\end{compactitem}


\newpage
\setlength{\bibitemsep}{1.8pt}

\begin{publications}
\printbib{phd}
\printbib{books}
\printbib{papers}
\printbib{chapters}
\printbib{conferences}
\printbib{inprogress}
\printbib{bookreviews}
\printbib{editorials}
\end{publications}

%\pagebreak

% Consulting reports
\setcounter{sumpapers}{0}
\label{consulting}
\printbibliography[heading=reports,type=report,keyword=consulting]%
\lastref{sumpapers}\addtocounter{sumpapers}{-1}%
\refstepcounter{sumpapers}\label{sumreports}

% Software
\newpage
\setcounter{sumpapers}{0}
\newrefcontext[sorting=ty]
\printbibliography[category=software,heading=software]\lastref{sumpapers}
\addtocounter{sumpapers}{-1}
\refstepcounter{sumpapers}\label{sumsoftware}

\end{document}
